Experiences in Modelling a Microcontroller Instruction Set Using B

### 2012-01-20 papers/ArticleZ80/source/paper.tex

We have developed a reusable set of basic definitions to model hardware concepts and data types
concepts. The models contains definitions to represent the: registers, interruptions, input and output
ports, memory and instructions. These definitions are grouped into separated development projects
and are available as libraries.

Thus the workspace is composed of modules group and libraries: 
\begin{itemize}

\item \textbf{Power}: it has the basics definitions to help the theorems
prover about simple calculus of power, especially power of two. It contains the definition of power function
and it has constants, that represent all required results of power function.

\item \textbf{Hardware Library}: it has the definition of bit vectors with size 8 and 16, basic functions to manipulate bit vectors and important assertions. This is presented in sections \ref{subsec:HardwareLibrary1}, \ref{subsec:HardwareLibrary2} and \ref{subsec:HardwareLibrary3}.

 \item \textbf{Types Library}: it has the definition of naturals and integers represented with  8 bits and 16 bits, basic conversion functions between the types and bit vectors and important assertions. This is presented in section \ref{subsec:Types}.

 \item \textbf{Platform}: it has the definition functions of arithmetic logic unit,  memory unit, registers and assembly instructions. This is presented in section \ref{sec:z80}.

 The corresponding dependency
diagram is depicted in Figure~\ref{fig:hardware-definition-graph}; information specific to each project is
presented in the following.

@@

The entities defined in the module $\textit{BIT\_DEFINITION}$ are the
type for bits, logical operations on bits (negation, conjunction,
disjunction, exclusive disjunction), as well as a conversion function
from Boolean to bit.

First, bits are modeled as a set of integers: $\textit{BIT} =
\textit{0..1}$. The negation is an unary function on bits and it is
defined as:

$
\begin{array}{l}
\textit{bit\_not}  \in  \textit{BIT}  \fun  \textit{BIT}  \land 
\textit{bit\_not} \rm = \rm \{ \rm 0  \mapsto  \rm 1 , \rm 1  \mapsto  \rm 0 \rm \}
\end{array}
$
%\forall ( \textit{bb}). (\textit{bb} \in \textit{BIT} \implies {bit\_not}(\textit{bb}) =1-\textit{bb})\\

The module also provides lemmas on negation that may be useful for the
users of the library to develop proofs:

$
\begin{array}{l}
%  \textit{bit\_not}(0) = 1;  \textit{bit\_not}(1) = 0; \\
\forall (\textit{bb}).(\textit{bb} \in \textit{BIT} \implies \textit{bit\_not}(\textit{bit\_not}(\textit{bb})) = \textit{bb})
\end{array}
$

Conjunction is a binary function on bits and it is defined as:

$
\begin{array}{l}
\textit{bit\_and} \in \textit{BIT} \times \textit{BIT} \fun \textit{BIT} \land \\
\forall (\textit{b1}, \textit{b2}).(\textit{b1}  \in \textit{BIT}  \land \textit{b2} \in \textit{BIT} \implies \\
\quad ((\textit{bit\_and}(\textit{b1}, \textit{b2}) = 1) \iff (\textit{b1} = 1)  \land  (\textit{b2} = 1)))
\end{array}
$

The module provides the following lemmas for commutativity and associativity:

$
\begin{array}{l}
%  \textit{bit\_and}(0,0) = 0;  \textit{bit\_and}(0,1) = 0; \\
%  \textit{bit\_and}(1,0) = 0;  \textit{bit\_and}(1,1) = 1; \\
\forall (\textit{b1},\textit{b2}).(\textit{b1} \in \textit{BIT} \land \textit{b2} \in \textit{BIT} \implies \\
\quad (\textit{bit\_and}(\textit{b1}, \textit{b2}) = \textit{bit\_and}(\textit{b2},\textit{b1})))\land \\
\forall (\textit{b1},\textit{b2},\textit{b3}).(\textit{b1} \in \textit{BIT} \land  \textit{b2} \in \textit{BIT} \land \textit{b3} \in \textit{BIT} \implies \\
\quad (\textit{bit\_and}(\textit{b1}, \textit{bit\_and}(\textit{b2},\textit{b3})) = \textit{bit\_and}(\textit{bit\_and}(\textit{b1},\textit{b2}),\textit{b3})))\\
% \forall (\textit{b1}).(\textit{b1} \in \textit{BIT} \implies (\textit{bit\_and}(\textit{b1}, 1) = \textit{b1})); \\
% \forall (\textit{b1}).(\textit{b1} \in \textit{BIT} \implies (\textit{bit\_and}(\textit{b1}, 0) = 0));
\end{array}
$

The module provides definitions of $\textit{bit\_or}$ (disjunction)
and $\textit{bit\_xor}$ (exclusive disjunction), as well as lemmas on
those operators. These are standard and their expression in B is
similar as for $\textit{bit\_and}$, they are thus omitted from this paper.

Finally, the conversion from Boolean to bit is simply defined as:

$
\begin{array}{l}
\textit{bool\_to\_bit} \in \BOOL \fun \textit{BIT} \land \textit{bool\_to\_bit} = \{ \TRUE \mapsto 1, \FALSE \mapsto 0 \} \\
\end{array}
$

Observe that all the lemmas that are provided in this module have been
mechanically proved by the theorem prover included with our B
development environment. None of these proofs requires human insight.

@@

Sequences are pre-defined in B, as functions whose the domain is an
integer range with lower bound 1 (one). Indices in bit vectors usually
range from 0 (zero) upwards and the model we propose obeys this
convention by making an one-position shift where necessary. This shift
is important to use the predefined functions of sequences. We thus
define bit vectors as non-empty sequences of bits, and
$\textit{BIT\_VECTOR}$ is the set of all such sequences:
$\textit{BIT\_VECTOR} = \seq1(\textit{BIT})$. The $\textit{BIT\_VECTOR}$ is an infinite set and it hinders the animation in ProB. 
To avoid this obstruction, the specialized types (\textit{BYTE} and \textit{BV16}) cannot reference directly \textit{BIT\_VECTOR}.

@@

We also define two functions $\textit{bv\_set}$ and $\textit{bv\_clear}$ that, given a bit vector, and a
position of the bit vector, return the bit vector resulting from setting the corresponding position to 0
or to 1, and a function $\textit{bv\_get}$ that, given a bit vector, and a valid position, each one
returns the value of the bit at that position. Only the first definition is shown here:

$
\begin{array}{l}
\textit{bv\_set} \in \textit{BIT\_VECTOR} \times \nat \fun \textit{BIT\_VECTOR} \land \textit{bv\_set} =\\
\lambda v, n . (v \in \textit{BIT\_VECTOR} \land n \in \nat \land n <\textit{size}(v)
\mid v \lover \{ n+1 \mapsto 1 \})
\end{array}
$

The function $bv\_catenate$ takes as parameters two bit vectors $v$ and $w$, and returns the result of the
concatenation of $v$ and $w$, such that $v$ constitutes the most significant part of the result.

@@

Additionally, the module provides definitions for the classical
logical combinations of bit vectors: $\textit{bit\_not}$,
$\textit{bit\_and}$, $\textit{bit\_or}$ and $\textit{bit\_xor}$. Only
the first two are presented here. Observe that the domain of the
binary operators is restricted to pairs of bit vectors of the same
length:

$
\begin{array}{l}
\textit{bv\_not} \in \textit{BIT\_VECTOR} \fun \textit{BIT\_VECTOR} \land \\
\textit{bv\_not} = \lambda v . (v \in \textit{BIT\_VECTOR} \mid \quad \lambda i . (1 .. \textit{size}(v)) \mid \textit{bit\_not}(v(i))) \land \\
\textit{bv\_and} \in \textit{BIT\_VECTOR} \times \textit{BIT\_VECTOR} \fun \textit{BIT\_VECTOR} \land \\
\textit{bv\_and} = \lambda v_1, v_2 . (v_1 \in \textit{BIT\_VECTOR} \land v_2 \in \textit{BIT\_VECTOR} \land \\
\textit{size}(v_1) = \textit{size}(v_2) \mid \lambda i . (1 .. \textit{size}(v_1)) \mid
\textit{bit\_and}(v_1(i), v_2(i)))
\end{array}
$

We provide several lemmas on bit vector operations. These lemmas
express properties on the size of the result of the operations
as well as classical algebraic properties such as associativity
and commutativity.

@@

Bit vectors of length 8 are bytes. They are a common entity in
hardware design. We provide the following definitions:

@@

The $\textit{BYTE\_INDEX}$ is the domain of the functions modeling bytes. It starts at 1 to obey a
definition of sequences from B. However, it is common in hardware architectures to start indexing from
zero. The definition $\textit{PHYS\_BYTE\_INDEX}$ is used to provide functionalities obeying this
convention. The $\textit{BYTE}$ type is as a specialized type of $\textit{BIT\_VECTOR}$, but it has a size
limit. Other specific definitions are provided to facilitate further modeling: the type $\textit{BV16}$
is created for bit vector of length 16 in a similar way.

@@

Bit vectors are used to represent and combine numbers: integer ranges (signed or unsigned). Therefore, our
library includes functions to manipulate such data, for example, the function $\textit{bv\_to\_nat}$ that
maps bit vectors to natural numbers:

$
\begin{array}{l}
\textit{bv\_to\_nat} \in \textit{BIT\_VECTOR} \fun \nat  \land \\
\textit{bv\_to\_nat} = \lambda v .  (v \in \textit{BIT\_VECTOR} \mid  \sum i . (i \in \dom(v) . v(i)
\times 2^{i-1}))
\end{array}
$

An  associated lemma is: $\forall n . (n \in \nat_1 \implies \textit{bv\_to\_nat}(\textit{nat\_to\_bv}(n)) = n)$

\subsection{Basics data types}

The instruction set architecture usually have common bit vector type and integer type.
In table~\ref{tab:types}, the first three are placed in the hardware library and the last four types are placed in the integer types library. 
Each type module has functions to manipulate and convert its data. There are seven common basic data types represented by modules.

\begin{table}
\caption{Details of basic data types}
\label{tab:types}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
 $Type\ Name$ & $Range$ & $Physical\ Size $  & $Associated\ Proof\ Obligations$ \\\hline
 BIT & 0..1 & 1 bit &   118 \\\hline %49 + 69 = 118 \\\hline
 BYTE & -- & 1 bytes &  153\\\hline%17 + 136 = 153\\\hline
 BV16 & -- & 2 bytes &  75 \\ \hline%5 + 70 = 75 \\ \hline
 UCHAR & 0..255 & 1 byte &  30 \\\hline %4 + 26 = 30 \\\hline
 SCHAR & -128..127 & 1 byte & 26 \\\hline %2 + 24 = 26 \\\hline
 USHORT & 0..65.535 & 2 byte & 62 \\\hline % 4 + 58 = 62 \\\hline
 SSHORT & -32.768..32.767 & 2 byte & 58\\\hline %  2 + 56 = 58\\\hline
%  &  & Total & 522\\\hline %  2 + 56 = 58\\\hline
\end{tabular}
\end{center}
\end{table}

Usually, each type module just needs to instantiate concepts that were already defined in the hardware
modeling library.  For example, the function $\textit{bv\_to\_nat}$ from bit vector arithmetic is
specialized to $\textit{byte\_uchar}$. As the set $\textit{BYTE}$ is a subset of the
$\textit{BIT\_VECTOR}$, this function can defined as follows:

$
\begin{array}{l}
\textit{byte\_uchar} \in \textit{BYTE} \fun \nat \land \\
\textit{byte\_uchar} = \lambda (v) . ( v \in BYTE | bv\_to\_nat(v) )
\end{array}
$

The definitions of the library types reuse the basic definitions from the hardware library. This provides
greater confidence and facilitates the proof process, because the prover can reuse the previously defined
lemma.

@@

% TODO: Adaptar para apenas fundamentar melhor o trabalho já desenvolvido. Citar o artigo SBMF e a dissertação. 
% Os meus trabalhos já desenvolvidos/ resultados atuais.
The next works quoted are directly related to the objective this paper.
The first work \cite{DantasSemish2008} shows the developed metodology to verify
software up to assembly level using B. A second work\cite{Dantas_SBMF08}
presents more details about the verification approach and a small example
software verified up to assembly level in three different platforms. 
The last work \cite{Valerio_SBMF09} shows a general view of the first version of Z80
model and techniques used in verification process.

%Link com o parágrafo anterior 
These works created a important step to software verification up to assembly
language, they show the actuals difficulties and suggest improvements in the
B tools.

@@

\subsubsection{Acknowledgements:} This experiment could not have succeeded without the interesting work of Michael Leuschel who developed several improvements in the ProB and provided important aid to enable the animation of the Z80 modeling.

>>>>

We have developed a reusable set of basic definitions to model
hardware concepts and data types concepts. The models contains
definitions to represent the: registers, interruptions, input and
output ports, memory and instructions. These definitions are grouped
into separated development projects and are available as libraries.
Thus the workspace is composed of the following: 
\begin{description}

\item[Power] contains the standard definition of exponentiation, as
  well as some basic properties, e.g. values of different powers of
  two. Given this definition, these properties have been proved
  interactively with the Atelier-B prover.

\item[Hardware Library] defines bit vectors with size 8 and 16, basic
  functions to manipulate bit vectors and important
  assertions. Details are given in sections
  \ref{subsec:HardwareLibrary1}, \ref{subsec:HardwareLibrary2} and
  \ref{subsec:HardwareLibrary3}.

\item[Types Library] defines sets of naturals and integers represented
  with 8 bits and 16 bits, basic conversion functions between those
  types and bit vectors, and important assertions. It is presented in
  section \ref{subsec:Types}.

\item[Platform] defines functions of the arithmetic logic unit, memory
  unit, registers and assembly instructions. Section \ref{sec:z80}
  provides additional details.

\end{description}

The dependencies between those libraries are depicted in
Figure~\ref{fig:hardware-definition-graph}.

@@

The entities defined in the module $\textit{BIT\_DEFINITION}$ are the
type for bits, logical operations on bits (negation, conjunction,
disjunction, exclusive disjunction), and a conversion function from
Booleans to bits.

We model bits as a set of integers: $\textit{BIT} =
\textit{0..1}$. The negation is an unary function on bits and it is
defined as:
$$
\begin{array}{l}
\textit{bit\_not}  \in  \textit{BIT}  \fun  \textit{BIT}  \land 
\textit{bit\_not} \rm = \rm \{ \rm 0  \mapsto  \rm 1 , \rm 1  \mapsto  \rm 0 \rm \}
\end{array}
$$
%\forall ( \textit{bb}). (\textit{bb} \in \textit{BIT} \implies {bit\_not}(\textit{bb}) =1-\textit{bb})\\

The module also provides lemmas on negation that may be useful for the
users of the library to develop proofs:
$$
\begin{array}{l}
%  \textit{bit\_not}(0) = 1;  \textit{bit\_not}(1) = 0; \\
\forall (\textit{bb}).(\textit{bb} \in \textit{BIT} \implies \textit{bit\_not}(\textit{bit\_not}(\textit{bb})) = \textit{bb})
\end{array}
$$
Conjunction is a binary function on bits and it is defined as:
$$
\begin{array}{l}
\textit{bit\_and} \in \textit{BIT} \times \textit{BIT} \fun \textit{BIT} \land \\
\forall (\textit{b1}, \textit{b2}).(\textit{b1}  \in \textit{BIT}  \land \textit{b2} \in \textit{BIT} \implies \\
\quad ((\textit{bit\_and}(\textit{b1}, \textit{b2}) = 1) \iff (\textit{b1} = 1)  \land  (\textit{b2} = 1)))
\end{array}
$$
The module provides the following lemmas for commutativity and associativity:
$$
\begin{array}{l}
%  \textit{bit\_and}(0,0) = 0;  \textit{bit\_and}(0,1) = 0; \\
%  \textit{bit\_and}(1,0) = 0;  \textit{bit\_and}(1,1) = 1; \\
\forall (\textit{b1},\textit{b2}).(\textit{b1} \in \textit{BIT} \land \textit{b2} \in \textit{BIT} \implies \\
\quad (\textit{bit\_and}(\textit{b1}, \textit{b2}) = \textit{bit\_and}(\textit{b2},\textit{b1})))\land \\
\forall (\textit{b1},\textit{b2},\textit{b3}).(\textit{b1} \in \textit{BIT} \land  \textit{b2} \in \textit{BIT} \land \textit{b3} \in \textit{BIT} \implies \\
\quad (\textit{bit\_and}(\textit{b1}, \textit{bit\_and}(\textit{b2},\textit{b3})) = \textit{bit\_and}(\textit{bit\_and}(\textit{b1},\textit{b2}),\textit{b3})))\\
% \forall (\textit{b1}).(\textit{b1} \in \textit{BIT} \implies (\textit{bit\_and}(\textit{b1}, 1) = \textit{b1})); \\
% \forall (\textit{b1}).(\textit{b1} \in \textit{BIT} \implies (\textit{bit\_and}(\textit{b1}, 0) = 0));
\end{array}
$$
The module provides definitions of $\textit{bit\_or}$ (disjunction)
and $\textit{bit\_xor}$ (exclusive disjunction), as well as lemmas on
those operators. These are standard and their expression in B is
similar as for $\textit{bit\_and}$.

Finally, the conversion from Boolean to bit is simply defined as:
$$
\begin{array}{l}
\textit{bool\_to\_bit} \in \BOOL \fun \textit{BIT} \land \textit{bool\_to\_bit} = \{ \TRUE \mapsto 1, \FALSE \mapsto 0 \} \\
\end{array}
$$
All the lemmas that are provided in this module have been
automatically proved by the prover of Atelier-B.

@@

Sequences are predefined objects in B and are natural candidate to
represent bit vectors. In B, sequences are functions whose the domain
is an integer range with lower bound 1 (one). Indices in bit vectors
usually range from 0 (zero) upwards and the model we propose obeys
this convention by making an offset where necessary, so that
predefined functions and proof rules may be used. We define bit
vectors as non-empty sequences of bits: $\textit{BIT\_VECTOR} =
\seq1(\textit{BIT})$. As $\textit{BIT\_VECTOR}$ is an infinite set,
this definition hinders the animation in ProB.  As a workaround, we
defined specialized types \textit{BYTE} and \textit{BV16} without
reference to \textit{BIT\_VECTOR}.

@@

We also define two functions $\textit{bv\_set}$ and
$\textit{bv\_clear}$ that, given a bit vector, and a position of the
bit vector, return the bit vector resulting from setting the
corresponding position to 1 and 0, and a function $\textit{bv\_get}$
that, given a bit vector and a valid position, returns the value of
the bit at that position. Only the first definition is shown here:
$$
\begin{array}{l}
\textit{bv\_set} \in \textit{BIT\_VECTOR} \times \nat \fun \textit{BIT\_VECTOR} \land \textit{bv\_set} =\\
\lambda v, n . (v \in \textit{BIT\_VECTOR} \land n \in \nat \land n <\textit{size}(v)
\mid v \lover \{ n+1 \mapsto 1 \})
\end{array}
$$

Function $bv\_catenate$ takes as parameters two bit vectors $v$ and
$w$, and returns the result of the concatenation of $v$ and $w$, such
that $v$ constitutes the most significant part of the result.

@@

Additionally, the module provides definitions for the classical
logical combinations of bit vectors: $\textit{bit\_not}$,
$\textit{bit\_and}$, $\textit{bit\_or}$ and $\textit{bit\_xor}$. Only
the first two are presented here. The domain of the binary operators
is restricted to pairs of bit vectors of the same length:
$$
\begin{array}{l}
\textit{bv\_not} \in \textit{BIT\_VECTOR} \fun \textit{BIT\_VECTOR} \land \\
\textit{bv\_not} = \lambda v . (v \in \textit{BIT\_VECTOR} \mid \quad \lambda i . (1 .. \textit{size}(v)) \mid \textit{bit\_not}(v(i))) \land \\
\textit{bv\_and} \in \textit{BIT\_VECTOR} \times \textit{BIT\_VECTOR} \fun \textit{BIT\_VECTOR} \land \\
\textit{bv\_and} = \lambda v_1, v_2 . (v_1 \in \textit{BIT\_VECTOR} \land v_2 \in \textit{BIT\_VECTOR} \land \\
\textit{size}(v_1) = \textit{size}(v_2) \mid \lambda i . (1 .. \textit{size}(v_1)) \mid
\textit{bit\_and}(v_1(i), v_2(i)))
\end{array}
$$
We provide several lemmas on bit vector operations. These lemmas
express properties on the size of the result of the operations
as well as classical algebraic properties such as associativity
and commutativity.

@@

Bytes, i.e. bit vectors of length 8, are a common entity in hardware
design. We provide the following definitions:

@@

$\textit{BYTE\_INDEX}$ is the domain of the functions modeling
bytes. It starts at 1 to be compatible with sequences. However, since
the hardware community starts indexing from zero, definition
$\textit{PHYS\_BYTE\_INDEX}$ provides functionalities obeying this
convention. Type $\textit{BYTE}$ is as a specialized type of
$\textit{BIT\_VECTOR}$, with a size constraint. Other specific
definitions are provided to facilitate further modeling: the type
$\textit{BV16}$ is created for bit vectors of length 16 in a similar
way.

@@

Bit vectors are used to represent and combine numbers: integer ranges
(signed or unsigned). Therefore, our library includes functions to
manipulate such data, for example, the function $\textit{bv\_to\_nat}$
maps bit vectors to natural numbers:
$$
\begin{array}{l}
\textit{bv\_to\_nat} \in \textit{BIT\_VECTOR} \fun \nat  \land \\
\textit{bv\_to\_nat} = \lambda v .  (v \in \textit{BIT\_VECTOR} \mid  \sum i . (i \in \dom(v) . v(i)
\times 2^{i-1}))
\end{array}
$$

An important lemma associated to this definition is: 
$$\forall n . (n \in \nat_1 \implies \textit{bv\_to\_nat}(\textit{nat\_to\_bv}(n)) = n).$$

\subsection{Basic data types}

The definition of instruction sets usually have bit vector and integer
types as listed in table~\ref{tab:types}. For each type, a number of
functions are defined, including conversion between different types.

\begin{table}
\caption{Details of basic data types}
\label{tab:types}
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
 \textit{Type\ Name} & \textit{Range} & \textit{Physical Size}  & \textit{Num. POs} & \textit{Library} \\\hline
 BIT & 0..1 & 1 bit &   118 & Hardware \\\hline %49 + 69 = 118 \\\hline
 BYTE & -- & 1 bytes &  153 & Hardware \\\hline%17 + 136 = 153\\\hline
 BV16 & -- & 2 bytes &  75 & Hardware \\ \hline%5 + 70 = 75 \\ \hline
 UCHAR & 0..255 & 1 byte &  30 & Types \\\hline %4 + 26 = 30 \\\hline
 SCHAR & -128..127 & 1 byte & 26 & Types \\\hline %2 + 24 = 26 \\\hline
 USHORT & 0..65.535 & 2 byte & 62 & Types \\\hline % 4 + 58 = 62 \\\hline
 SSHORT & -32.768..32.767 & 2 bytes & 58 & Types \\\hline %  2 + 56 = 58\\\hline
%  &  & Total & 522\\\hline %  2 + 56 = 58\\\hline
\end{tabular}
\end{center}
\end{table}

Usually, each type module just needs to specialize definitions that
are given in the hardware modeling library.  For example, the function
$\textit{bv\_to\_nat}$ from bit vector arithmetic is specialized to
$\textit{byte\_uchar}$. As the set $\textit{BYTE}$ is a subset of the
$\textit{BIT\_VECTOR}$, this function can defined as follows:
$$
\begin{array}{l}
\textit{byte\_uchar} \in \textit{BYTE} \fun \nat \land \\
\textit{byte\_uchar} = \lambda (v) . ( v \in BYTE | bv\_to\_nat(v) )
\end{array}
$$

The definitions of the library types reuse the basic definitions from
the hardware library. This provides greater confidence and facilitates
the proof process, because the prover can reuse the previously defined
lemmas.

@@

% TODO: Adaptar para apenas fundamentar melhor o trabalho já desenvolvido. Citar o artigo SBMF e a dissertação. 
% Os meus trabalhos já desenvolvidos/ resultados atuais.
The next works quoted are directly related to the objective this paper.
The first work \cite{DantasSemish2008} shows the developed metodology to verify
software up to assembly level using B. A second work\cite{Dantas_SBMF08}
presents more details about the verification approach and a small example
software verified up to assembly level in three different platforms. 
The last work \cite{Valerio_SBMF09} shows a general view of the first version of Z80
model and techniques used in verification process.
%Link com o parágrafo anterior 
These works created a important step to software verification up to assembly
language, they show the actuals difficulties and suggest improvements in the
B tools.

@@

\subsubsection{Acknowledgements:} The animation of the model would not
have been possible without the help of Michael Leuschel who kindly
provided feedback and developed several improvements to ProB to meet our
needs.
